Light Transport Techniques for Tensor Field Visualization

### 2019-07-28 beamer2thesis/dummy.tex
update

\usepackage{color}
\usepackage{graphicx}
\usepackage{fancybox}

@@

%\color{unirot}{sebibek@gmail.com}
%\newsubfloat{figure}
\newcommand{\source}[1]{\hspace{-3pt} {\tiny \raisebox{-0.75in}{\rotatebox[origin=t]{90}{Source: \color{black}{#1}}}}}
\setlength{\belowcaptionskip}{-10pt}
%\setlength{\intextsep}{-30pt}

@@

%\frame[plain]{\titlepage}
\frame{
\frametitle{{Finite-Time Lyapunov exponents}}

\begin{columns}
\begin{column}{.5\textwidth}
\begin{small}
\begin{block}{\centering \textbf{Definition}}
Local: 
$
	\sigma = \frac{1}{\lvert T\rvert}\ln \frac{\Delta}{\delta}
$\\
Global: 
$
	\sigma(\mathbf{x})=\frac{1}{\lvert T\rvert}\ln \|\nabla\mathbf{\upvarphi(x)}\|_2
$\\
{\scriptsize whereas $\| A\| _2 = \sqrt{\lambda_{max}(A^TA)}$ is the spectral norm of matrix $A$}
\end{block}
\end{small}
\begin{itemize}
	\item measure for separation abilities of LTV (time-variant) systems concerning massless tracer particles
	\item Lagrangian view in vector fields: placing two close-by particles into and moving with the flow
\end{itemize}

\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\begin{minipage}{0.85\textwidth}
\centering
\includegraphics[height=0.6\textwidth]{gyre_rot.pdf} a)
\includegraphics[height=0.6\textwidth]{ftle_sep.pdf} b)
\caption{a) Vector field, b) diverging pathlines}
\end{minipage}
\begin{minipage}{0.1\textwidth}
\source{b) Skript Prof. Sadlo, SciVis SS2017}
\end{minipage}

\end{figure}

\end{column}
\end{columns}
} % END OF FRAME

\frame{
\frametitle{{Finite-Time Lyapunov exponents}}

\begin{columns}
\begin{column}{.5\textwidth}
\begin{small}
\begin{block}{\centering \textbf{Definition}}
Local: 
$
	\sigma = \frac{1}{\lvert T\rvert}\ln \frac{\Delta}{\delta}
$\\
Global: 
$
	\sigma(\mathbf{x})=\frac{1}{\lvert T\rvert}\ln \|\nabla\mathbf{\upvarphi(x)}\|_2
$\\
{\scriptsize whereas $\| A\| _2 = \sqrt{\lambda_{max}(A^TA)}$ is the spectral norm of matrix $A$}
\end{block}
\end{small}
\begin{itemize}
	\item measure for separation abilities of LTV (time-variant) systems concerning massless tracer particles
	\item Lagrangian view in vector fields: placing two close-by particles into and moving with the flow
\end{itemize}

\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\centering
\includegraphics[height=0.35\textwidth]{gyre.pdf}~a)
\includegraphics[height=0.35\textwidth]{ftle.png}~b)
\caption{a) Vector field, b) FTLE field}

\end{figure}

\end{column}
\end{columns}
} % END OF FRAME

>>>>

\usepackage{color}
\usepackage{graphicx}
\usepackage{fancybox}
\usepackage[singlespacing]{setspace}

@@

%\color{unirot}{sebibek@gmail.com}
%\newsubfloat{figure}
\newcommand{\source}[1]{\hspace{-3pt} {\tiny \raisebox{-0.75in}{\rotatebox[origin=t]{90}{Source: \color{black}{#1}}}}}
\setlength{\belowcaptionskip}{-10pt}
\setlength{\intextsep}{-20pt}

@@

%\frame[plain]{\titlepage}

\frame{
\frametitle{{Propagation Scheme - Physical Model}}
\begin{block}{\centering \textbf{Crystal Fiber Structures}}
\begin{itemize}
	\item crystal lattices reveal gradients dependent on direction, which leads to anisotropic light transport inside the medium (birefringence)
	\item the propability for redistribution of a photon in a particular direction is given by the phase function model yielded from Rayleigh scattering:
	\begin{align*}
 	P(\omega) &= \frac{T(\omega)}{\int_{k\pi}^{(k+1)\pi}T(\omega)\mathop{d\omega}}\\
 	\mathit{with} \int_0^{\pi} P(\omega) &= 1.
	\end{align*}
	\item each tensor is then a unique footprint: $t_{i,j}\mapsto T(\omega)$
\end{itemize}
\end{block}
} % END OF FRAME
